Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2019-01-23 automatica/paper.tex
fix section label

\subsection{Safety of closed-loop systems}

@@

%While in the previous section we have discussed the generic CEGIS framework, 
We are now equipped to apply the general CEGIS framework to the synthesis of digital controllers. 
We start by describing the property that we pass to the synthesizer as the specification $\phi$. 
Namely, as we are interested in capturing safety (to be discussed in Section~\ref{ssec:safespecification}\note{fix?}),  
we use a stability specification to narrow the search space of possible controllers, as detailed in Section~\ref{ssec:stabspecification}.

>>>>

\subsection{Safety of closed-loop systems}
\label{sec:safety}

@@

%While in the previous section we have discussed the generic CEGIS framework, 
We are now equipped to apply the general CEGIS framework to the synthesis of digital controllers. 
We start by describing the property that we pass to the synthesizer as the specification $\phi$. 
Namely, as we are interested in capturing safety (as discussed in Section~\ref{sec:safety}),  
we use a stability specification to narrow the search space of possible controllers, as detailed in Section~\ref{ssec:stabspecification}.
